Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-20 talk/iwtc11/paper.tex
remove sections about numpy and prolog for space reasons

\subsection{Numpy}

As a part of the PyPy project, we implemented small numerical kernel for
performing matrix operations. The exact extend of this kernel is besides
the scope of this paper, however the basic idea is to unroll a series of
array operations into a loop compiled into assembler. LICM is a very good
optimization for those kind of operations. The example benchmark performs
addition of five arrays, compiling it in a way that's equivalent to C's:

%\begin{figure}
\begin{lstlisting}[mathescape,basicstyle=\setstretch{1.05}\ttfamily\scriptsize]
for (int i = 0; i < SIZE; i++) {
   res[i] = a[i] + b[i] + c[i] + d[i] + e[i];
}
\end{lstlisting}
%\end{figure}

Where $res$, $a$, $b$, $c$, $d$ and $e$ are $double$ arrays.

\subsection{Prolog}
XXX: Carl?

>>>>

XXX add a small note somewhere that numpy and prolog are helped by this
optimization
